\LARGE \bf {\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-02-28 paper.tex
Update on Overleaf.

When perception modules provide objects localisation, the physical consistency
of the locations is not typically enforced. For instance, objects that are
supposed to lay on a table might be slightly above (or inset into) the table; or
when dropping an item into a box, the robot can not update the location of the
item anymore as it becomes occluded.

These issues can be alleviated by relying on a physics simulation to stabilise
the position of objects: natural physics (including gravity) are simulated for a
short amount of time (up to one second) ahead of time, and the objects'
positions are updated accordingly. To this end, \uwds provide a standard filter,
the {\tt physics\_filter}, based on the Bullet RT physics simulation and the
{\tt pybullet}\footnote{\url{https://pybullet.org/}} library. It generates an
output world that mirrors its input world after a specific duration of physics
simulation,  the physical properties of objects (including mass, friction,
inertia) being provided from standard URDF descriptions.

@@

\uwds is being used within the European L2TOR project~\cite{belpaeme2015l2tor} as part of a system for a large scale study with 150 children. \uwds {\tt spatial\_relations} module is used to visualise counting tasks and teach spatial words for a second language. \uwds's loose coupling allows for easy integration with the {\tt spatial_relations} between either an object recognition system that would allow for use in a physical environment(Figure~\ref{fig|l2torexample})

>>>>

When perception modules provide objects localization, the consistency is not guarantee, objects on a table seem to slightly flight in the air, when dropping them in a bin the localization is not updated any more when the objects are occulted, resulting in objects that fly just above the bin.

Being able to manage that issues by simulating the gravity is the purpose of a dedicated client  
{\tt physics filter} that have been designed using Bullet RT physics simulation and pybullet \url{https://pybullet.org/} library, it provides from an input world, an output world where objects described by an URDF file are filtered by the simulator, which gives us the near future of the objects based on their position, mass and inertia.

@@

\uwds is being used within the European L2TOR project~\cite{belpaeme2015l2tor} as part of a system for a large scale study with 150 children. \uwds {\tt spatial\_relations} module is used to visualise counting tasks and teach spatial words for a second language. \uwds's loose coupling allows for easy integration with the {\tt spatial_relations} between either an object recognition system that would allow for use in a physical environment(
